Is Information Ontological or Physical, or Is It Perhaps Something Else? Some Remarks on Krzanowski's Approach to the Concept of Information

### 2023-02-03 ART_Mscislawski/Mscislaw.tex
Olszewski article added

\section{Introduction}
This article primarily aims to concisely present Roman Krzanowski's approach to the concept of \textit{physical information.} This concept is perceived here as a~kind of ``intermediate concept'' that can act as a~bridge to the development of his concept of \textit{ontological information}
%\label{ref:RNDVGZ8jlBX2V}(cf. Krzanowski, 2020a; 2020b; 2020c; 2022),
\parencites[cf.][]{krzanowski_does_2020}[][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[and especially][]{krzanowski_ontological_2022},%
and can be regarded as a~special case of the latter. Indeed, we believe that the latter concept inherits many characteristics from the former, but not all the issues have been solved.\footnote{It is also worth mentioning that in some works, Krzanowski seems to use these two terms (i.e., physical and ontological information) interchangeably
%\label{ref:RNDx2sgo6ehaO}(cf. Krzanowski, 2020b).
\parencite[cf.][]{krzanowski_what_2020}.%
} This situation implies that we are dealing with a~truly fundamental issue here, namely the fundamentality of the concept of information. Furthermore, this paper also aims to discuss some of this concept's interesting properties and present possible avenues for further developing this interesting proposal. It is well known that there is enormous interest in the philosophical aspects of the concept of information 
%\label{ref:RNDKUzkfsqSdA}(e.g. Adriaans and Benthem, 2008; Burgin, 2010; Floridi, 2011; Dodig Crnkovic and Burgin, 2019),
\parencites[e.g.,][]{adriaans_philosophy_2008}[][]{burgin_theory_2010}[][]{floridi_philosophy_2011}[][]{dodig_crnkovic_philosophy_2019}, %
 but we feel that Krzanowski's proposal is particularly attractive with some great research potential, especially for studying physical reality. It would %
therefor be helpful, in our opinion, to position this concept within the vast array of philosophical problems related to the notion of information, as well as introduce a~few distinctions to allow us to order the discourse.

>>>>

\section{Introduction}
This article primarily aims to concisely present Roman Krzanowski's approach to the concept of \textit{physical information.} This concept is perceived here as a~kind of ``intermediate concept'' that can act as a~bridge to the development of his concept of \textit{ontological information}
%\label{ref:RNDVGZ8jlBX2V}(cf. Krzanowski, 2020a; 2020b; 2020c; 2022),
\parencites[cf.][]{krzanowski_does_2020}[][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[and especially][]{krzanowski_ontological_2022},%
and can be regarded as a~special case of the latter. Indeed, we believe that the latter concept inherits many characteristics from the former, but not all the issues have been solved.\footnote{It is also worth mentioning that in some works, Krzanowski seems to use these two terms (i.e., physical and ontological information) interchangeably
%\label{ref:RNDx2sgo6ehaO}(cf. Krzanowski, 2020b).
\parencite[cf.][]{krzanowski_what_2020}.%
} This situation implies that we are dealing with a~truly fundamental issue here, namely the fundamentality of the concept of information. Furthermore, this paper also aims to discuss some of this concept's interesting properties and present possible avenues for further developing this interesting proposal. It is well known that there is enormous interest in the philosophical aspects of the concept of information 
%\label{ref:RNDKUzkfsqSdA}(e.g. Adriaans and Benthem, 2008; Burgin, 2010; Floridi, 2011; Dodig Crnkovic and Burgin, 2019),
\parencites[e.g.,][]{adriaans_philosophy_2008}[][]{burgin_theory_2010}[][]{floridi_philosophy_2011}[][]{dodig_crnkovic_philosophy_2019}, %
 but we feel that Krzanowski's proposal is particularly attractive with some great research potential, especially for studying physical reality. It would %
therefore be helpful, in our opinion, to position this concept within the vast array of philosophical problems related to the notion of information, as well as introduce a~few distinctions to allow us to order the discourse.
